Effect of Election on Currency Fluctuation

### 2024-04-14 paper/paper.qmd
added file location for datasheet in the READMe and answered datasheet questions up to "Collection Process"

library(tidyverse)
library(readr)
library(rstanarm)
library(knitr)
library(modelsummary)
library(ggplot2)
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

-   $y_i$ is the daily exchange rate of USD v.s. CAD (base unit is CAD = 1)

>>>>

library(tidyverse)
library(readr)
library(rstanarm)
library(knitr)
library(modelsummary)
library(ggplot2)
library(arrow)
```

@@

```{r}
#| label: fig-exchange
#| fig-cap: Exchange Rate from 1971 to 2024
#| echo: false

exchange_inaug <- read_csv(here::here("data/analysis_data/exchange_inaug.csv"), show_col_types = FALSE)

exchange_inaug |>
  ggplot(aes(
    x = date,
    y = exchange_rate
  )) +
  geom_line() +
  labs(
    x = "Year",
    y = "Exchange Rate: USD to CAD (Base Currency: USD)",
    title = "Exchange Rate from 1971 to 2024"
  )
```

@@

-   $y_i$ is the daily exchange rate of USD v.s. CAD (base unit is USD = 1)
